### 2019-03-18 thesis_proposal_1/main.tex
another draft

>>>>

Carbon nano-wires are versatile materials composed of carbon chains with a wide range of applications due to the  //

Over the last couple of decades, Carbon Nanowires (CNWs) have found important applications in the field of rapid label-free biosensing platforms for their excellent electrical, thermal and chemical properties. Despite the growing interest in incorporating these materials into sensitive analytical devices, there has been limited research efforts that explore the realistic incorporation of these structures into broader microsystems. The present dissertation explores two Advanced Additive Manufacturing (AdAM) techniques for the fabrication of CNWs with promising characteristics for sensing applications. The first technique, Electro-Mechanical Spinning (EMS) is a relatively new method for the production of CNWs with highly-oriented patterning capabilities, and is assessed in terms of the minimum feature sizes that it can attain reproducibly. The second method, Multiple Photon Polymerization (MPP) is a mature laser manufacturing technique that offers high repeatability, yet it has remained largely unexplored in the field of carbon materials. This work presents a study of how MPP can be used to create CNWs in terms of micro-fabrication parameters like laser power and scanning velocity. A thorough review study of the surface properties required for carbon materials to become eligible candidates in biosensing is also included in this dissertation. Lastly, an application of CNWs is presented, in which a Joule Heating technique is used to induce controlled breaking of the wires to produce nano-scale separated carbon electrodes, which hold potential for micro/nano particle manipulation in microfluidics. //
